Type Refinements for the Working Class

### 2015-11-12 paper.tex
Define functional equality

%% Functional equality $\HRMemEq{\Phi}{\Psi}{M}{N}{\phi}$ is defined by
%% induction on the evidence for its presupposition
%% $\PRefinesCtx{\Phi}{\Psi}{\Gamma}$:
%% \begin{gather*}
%%   \infer{
%%     \HRMemEq{\Phi}{\cdot}{M}{N}{\phi}
%%   }{
%%     \RMemEq{\Phi}{M}{N}{\phi}
%%   }\qquad
%%   \infer{
%%     \HRMemEq{\Phi}{\Psi,x:\psi}{M}{N}{\phi}
%%   }{
%%  }
%%\end{gather*}

%%
%% \subsection{Parametric functional equality}
%%
%% Next, we will define the parametric hypothetico-general (or \emph{functional})
%% equality
%% $\IMode{\Phi}\parallel\IMode{\Psi}\vDash\IMode{M}=\IMode{N}\in\IMode{\phi}$
%% simultaneously with variable context well-formedness,
%% $\IMode{\Phi}\parallel\RefinesCtx{\Psi}{\Gamma}$.

>>>>

Functional equality $\HRMemEq{\Phi}{\Psi}{M}{N}{\phi}$ presupposes
$\RefinesCtx{\Phi}{\Upsilon}$, $\PRefinesCtx{\Phi}{\Psi}{\Gamma}$,
$\HRefines{\Phi}{\Psi}{\phi}{\tau}$, $\IsAbt{\cdot}{\Upsilon}{\Gamma}{M}{\tau}$
and $\IsAbt{\cdot}{\Upsilon}{\Gamma}{N}{\tau}$; the judgment is defined by
induction on the evidence for the second presupposition
$\PRefinesCtx{\Phi}{\Psi}{\Gamma}$:

\paragraph{Case} $\DefPRefinesCtxNil{\Phi}$.
\[
  \infer{
    \HRMemEq{\Phi}{\cdot}{M}{N}{\phi}
  }{
    \RMemEq{\Phi}{M}{N}{\phi}
  }
\]

\paragraph{Case} $\DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\psi}{\Gamma}{\sigma}$,
where $\RefinesCtx{\Phi}{\Upsilon}$.
\[
  \infer{
    \HRMemEq{\Phi}{\Psi,x:\psi}{M}{N}{\phi}
  }{
    \HPGenJ{\Upsilon}{\Gamma}{\MV{m},\MV{n}:\sigma}{
      \HypJ{
        \HRMemEq{\Phi}{\Psi}{
          \Subst{\MV{m}}{x}{\phi}
        }{
          \Subst{\MV{n}}{x}{\psi}
        }{\phi}
      }{
        \HRMemEq{\Phi}{\Psi}{\MV{n}}{\MV{n}}{\psi}
      }
    }
  }
\]
